%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cvpub
{Mechanical Net} % Organization
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Collected massive 3D mechanical component CAD data with a web-scrapper and expanded the data for dense data distribution using Creo Parametric and SolidWorks API. Also, developed a web-based 3D CAD search engine using a 3D Deep Neural Network and PostgreSQL database.}
\end{cvitems}
}

\cvpub
{FuseNet} % Organization
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a Generative Adversarial Network which generates 3D objects given a discrete category condition and continuous instance-level attributes. Developed a 3D data pre-processing program which converts 3D data to various types of geometric tensors. (\textit{Relevant publication: [C1]})}
\end{cvitems}
}

%------------------------------------------------

\cvpub
{Latent Transformation Neural Network (LTNN)} % Organization
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a fully-convolutional conditional generative network which is capable of view synthesis using a light-weight neural network suited for real-time applications. (\textit{Relevant publication: [J3]})}
\end{cvitems}
}

%------------------------------------------------    

\cvpub
{Visual Programming Language for Mobile Robots and IoT} % Job title
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Proposed a web-based visual and spatial programming language that allows novice users and small industries to program mobile robots and IoT Nodes to execute planned tasks. Developed a virtual world using ROS with Python and GAZEBO for simulating the spatial programming language.}
\end{cvitems} 
}

%------------------------------------------------

\cvpub
{ControllAR} % Job title
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Proposed a parametrizing interface, simple and accessible fabrication workflow, and a pressure sensor using a soft piezoresistive elastomer material. Also, developed embedded system using Arduino and analyzed signals from different sensors and materials. (\textit{Relevant publication: [J2]})}
\end{cvitems}
}

\cvpub
{3D Objects Classification Model Evaluation} % Organization
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Proposed an evaluation method for 3D Deep Neural Networks by visualizing the impact of each voxel of each 3D objects. Developed a web-based CAD data retrieval engine for demonstration. (\textit{Relevant publication: [J1]})}
\end{cvitems}
}

\cvpub
{Office Automation Platform} % Organization
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed an office automation system using Python specifically for triggering the events such as sending an e-mail or issuing receipts. Also, Designed a PostgreSQL database for customer web-service. (\textit{Relevant patent: [P1]})}
\end{cvitems}
}

\cvpub
{Web-based Surgical Workflow Management Platform} % Organization
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a web-based interface and database for integrated surgical information, to optimize surgical procedures and reduce the medical loss caused by communication errors and lack of information.}
\end{cvitems}
}
%------------------------------------------------

\end{cventries}