%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Selected Publications / Patents}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------
\cvpub
{Publications} % Title
{ % Description(s)
\begin{cvitems}
    \item {[\textbf{14}] \textit{DiceHuBERT: Distilling HuBERT with a Self-Supervised Learning Objective} \newline
            \hspace{1.5em} \textbf{H Chi}, Z Aldeneh, T Likhomanenko, O Rudovic, T Higuchi, L Chen, S Watanabe, A Abdelaziz,
        \textbf{Interspeech}, 2025.}
    \item {[\textbf{13}] \textit{Adaptive Knowledge Distillation for Device-Directed Speech Detection} \newline
            \hspace{1.5em} \textbf{H Chi}, F Pesce, W Chang, O Rudovic, A Argueta, S Barun, V Garg, A Abdelaziz,  \textbf{Interspeech}, 2025.}
    \item {[\textbf{12}] \textit{Context-Enriched Voxel Queries for Camera-based 3D Occupancy Prediction} \newline
            \hspace{1.5em} G Oh, S Kim, H Ko, \textbf{H Chi}, J Kim, D Lee, D Ji, S Choi, S Jang, S Kim,
        Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}) 2025.}
    % \item {[\textbf{4}] \textit{CARING-AI: Context-aware Augmented Reality INstruction through Generative Artificial Intelligence} \\
    %             J Shi, R Jain, S Chi, H Doh, \textbf{H Chi}, AJ Quinn, K Ramani \\
    %     \textbf{CHI 2025}.}
    \item {[\textbf{11}] \textit{InfoGCN++: Learning Representation by Predicting the Future for Online Skeleton-based Action Recognition}\newline
        \hspace{1.5em} \textbf{H Chi*}, S Chi*, Q Huang, K Ramani, 
        Transactions on Pattern Analysis and Machine Intelligence (\textbf{TPAMI}) 2024.}
    \item {[\textbf{10}] \textit{M2D2M: Discrete Diffusion Model for the Multi-Motion Generation from the Text} \newline
        \hspace{1.5em} \textbf{H Chi*}, S Chi*, H Ma, N Agarwal, F Siddiqui, K Ramani, K Lee,
        European Conference on Computer Vision (\textbf{ECCV}) 2024.}
    \item {[\textbf{9}] \textit{Enhanced Motion Forecasting with Visual Relation Reasoning} \newline
        \hspace{1. em}  S Kim, H Baek, S Lee, \textbf{H Chi}, H Lim, J Kim, S Kim,
        European Conference on Computer Vision (\textbf{ECCV}) 2024.}
    \item {[\textbf{8}] \textit{VisionTrap: Vision-Augmented Trajectory Prediction Guided by Textual Descriptions}\newline
        \hspace{1. em}S Moon, H Woo, H Park, H Jung, R Mahjourian, \textbf{H Chi}, H Lim, S Kim, J Kim,
        European Conference on Computer Vision (\textbf{ECCV}) 2024.}
    \item {[\textbf{7}] \textit{Multi-Modal Representation Learning with Tactile Modality} \newline
        \hspace{1. em}\textbf{H Chi*}, J Barreiros*, J Mercat, K Ramani, T Kollar,
        International Conference on Intelligent Robots and Systems (\textbf{IROS}) 2024.}
    \item {[\textbf{6}] \textit{Higher-order Relation Reasoning for Trajectory Prediction}\newline
        \hspace{1. em}S Kim, \textbf{H Chi}, H Lim, K Ramani, J Kim, S Kim,
        Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}) 2024.}
    \item {[\textbf{5}] \textit{AdamsFormer for Spatial Action Localization in the Future} \newline
        \hspace{1. em}\textbf{H Chi}, K Lee, N Agarwal, Y Xu, K Ramani, C Choi,
        Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}) 2023.}
    \item {[\textbf{4}] \textit{Uncovering the Missing Pattern: Unified Framework Towards Trajectory Imputation and Prediction} \newline
        \hspace{1. em} X Yi, A Bazarjani, \textbf{H Chi}, C Choi, Y Fu,
        Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}) 2023.}
    \item {[\textbf{3}] \textit{Pose Relation Transformer: Refine Occlusions for Human Pose Estimation} \newline
        \hspace{1. em}\textbf{H Chi*}, S Chi*, C Stanley, K Ramani,
        International Conference on Robotics and Automation (\textbf{ICRA}) 2023.}
    \item {[\textbf{2}] \textit{InfoGCN: Representation Learning for Human Skeleton-based Action Recognition} \newline
        \hspace{1. em}\textbf{H Chi*}, MH Ha*, S Chi, SW Lee, Q Huang, K Ramani, 
        Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}) 2022.}
    \item {[\textbf{1}] \textit{A Large-scale Annotated Mechanical Components Benchmark for Classification and Retrieval Tasks with Deep Neural Networks} \newline
        \hspace{1. em}\textbf{H Chi*}, S Kim*, X Hu, Q Huang, K Ramani,
        European Conference on Computer Vision (\textbf{ECCV}) 2020.}
\end{cvitems}
}


% \item {[\textbf{6}] \textit{Functional Hand Type Prior for 3D Hand Pose Estimation \& Action Recognition from
% Egocentric View Monocular Videos,W Roh, SH Lee, WJ Ryoo, J Lee, G Oh, S Hwang, \textbf{H Chi}, S Kim,
%      \textbf{BMVC (Oral) 2023}.}
% \item {[\textbf{C1}] Kim et al, \textit{First-Person View Hand Segmentation of Multi-Modal Hand Activity Video Dataset}, \textbf{BMVC}, 2020.}
% \item {[\textbf{C13}] Seo et al, \textit{Egocentric View Hand Action Recognition by Leveraging Hand Surface and Hand Grasp Type}, \textit{ICPRAI}, 2024. }
% \item {[\textbf{J9}] Kim et al, \textit{Enhanced fringe-to-phase framework using deep learning}, \textbf{Image and Vision Computing}, 2024.}
% \item {[\textbf{J7}] Lee et al, \textit{Deep Learning-Assisted Design of Bilayer Nanowire Gratings for High-Performance MWIR Polarizers, \textbf{Advanced Materials Technologies}, 2024. }
% \item {[\textbf{J6}] Lee et al, \textit{Robust Sound-Guided Image Manipulation}, \textbf{Neural Networks}, 2024.}
% \item {[\textbf{J5}] Unmesh et al, \textit{Interacting Objects: A dataset of object-object interactions for richer dynamic scene representations}, \textbf{RA-L}, 2024.}
% \item {[\textbf{J4}] Kim et al, \textit{3D CAD Model Simplification for Mechanical Parts Using Generative Adversarial Networks}, \textbf{Computer-Aided Design}, 2023.}
% \item {[\textbf{J3}] Kim et al, \textit{Object synthesis by learning part geometry with surface and volumetric representations}, \textbf{Computer-Aided Design}, 2021.}
% \item {[\textbf{J2}] Kim et al, \textit{Latent transformations neural network for object view synthesis}, \textbf{The Visual Computer}, 2019.}
% \item {[\textbf{J1}] Hwang et al, \textit{An Evaluation Methodology for 4D Deep Neural Network using Visualization in 3D Data Classification}, \textbf{JMST}, 2019.}
%
% \vspace{-.5em}
\cvpub
{Patents}{
\begin{cvitems}
\item {[\textbf{P7}] \textit{Multi-Motion Generation}, \newline
        \hspace{1.8em}S Chi, \textbf{H Chi}, F Siddiqui, N Agarwal, H Ma, K Lee, US Patent App.}
\item {[\textbf{P6}] \textit{System and Method for Authoring Context-augmented Reality Instruction through Generative Artificial Intelligence},\newline
        \hspace{1.8em} K Ramani, S Chi, \textbf{H Chi}, R Jain, J Shi, US Patent App.}
\item {[\textbf{P5}] \textit{Pose Relation Transformer Refine Occlusions for Human Pose Estimation},\newline
        \hspace{1.8em} K Ramani, \textbf{H Chi}, S Chi, US Patent App. 18/584,191.}
\item {[\textbf{P4}] \textit{Spatio Action Localization in the Future}, \newline
        \hspace{1.8em}\textbf{H Chi}, K Lee, N Agarwal, Y Xu, C Choi, US Patent App. 18/300,844.}
\item {[\textbf{P3}] \textit{Trajectory Imputation and Prediction},\newline
        \hspace{1.8em} Y Xu, A Bazarjani, \textbf{H Chi}, C Choi, US Patent App. 18/182,195. }
\item {[\textbf{P2}] \textit{Pixel-wise Hand Segmentation of Multi-modal Hand Activity Video Dataset},\newline
        \hspace{1.8em} K Ramani, S Kim, \textbf{H Chi},  US Patent 11,562,489.}
\item {[\textbf{P1}] \textit{Computer Input System for Office/Factory Automation}, \newline
        \hspace{1.8em}\textbf{H Chi}, WO Patent 2018/074729 A1.}
\end{cvitems}
}


\end{cventries}
