%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications and Patents}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cvpub
{Conference Papers} % Title
{ % Description(s)
\begin{cvitems}
\item {[C1] S. Kim, \textbf{H. G. Chi} and Karthik Ramani. "FuseNet:Fusing surface and volumetric representations for 3D Shape Synthesis and Analysis" (2019) \textit{International Conference on Computer Vision (ICCV)}, submitted.}
\end{cvitems}
}

%------------------------------------------------

\cvpub
{Journal Papers} % Title
{ % Description(s)
\begin{cvitems}
\item {[J3] S. Kim, N. Winovich, \textbf{H. G. Chi}, G. Lin and and Karthik Ramani. "Latent Transformations Neural Network for Object View Synthesis" (2019) \textit{The Visual Computer}, submitted.}
\item {[J2] L.Paredes, X. Qian, \textbf{H. G. Chi} and Karthik Ramani. "ControllAR: Design and Fabrication of a Universal Parametric Low-Profile Hand Wearable for Augmented Reality Interactions" (2019) \textit{Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies (IMWUT)}, under revision.}
\item {[J1] H. T. Hwang, \textbf{H. G. Chi}, N. K. Kang, H. B. Kong and Soo-Hong Lee. “An Evaluation Methodology for 3D Deep Neural Network using Visualization in 3D Data Classification” (2019) \textit{Journal of Mechanical Science and Technology (JMST)}, 33(3), 1333-1339.}
\end{cvitems}
}

\cvpub
{Patents} % Title
{ % Description(s)
\begin{cvitems}
\item {[P1] \textbf{H. G. Chi}.  “Computer Input Automation System” KR Patent (2017): 10-1745330}
\end{cvitems}
}


%------------------------------------------------

\end{cventries}