%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Selected Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
\vspace{-1em}
%------------------------------------------------
\cvpub
{} % Title
{ % Description(s)
\begin{cvitems}
    % \item {Chi et al, ``DiceHuBERT: Distilling HuBERT with a Self-Supervised Learning Objective", \textbf{Interspeech}, 2025, submitted.}
    % \item {Chi et al, ``Adaptive Knowledge Distillation for Device-Directed Speech Detection", \textbf{Interspeech}, 2025, submitted.}
    \item {Kim et al, ``Context-Enriched Voxel Queries for Camera-based 3D Occupancy Prediction", \textbf{CVPR}, 2025.}
    \item {Chi et al, ``InfoGCN++: Learning Representation by Predicting the Future for Online Skeleton-based Action Recognition", \textbf{TPAMI} 2024. }
    \item {Chi et al, ``M2D2M: Discrete Diffusion Model for the Multi-Motion Generation from the Text", \textbf{ECCV}, 2024.}
    \item {Kim et al, ``Enhanced Motion Forecasting with Visual Relation Reasoning", \textbf{ECCV}, 2024.}
    \item {Moon et al, ``VisionTrap: Vision-Augmented Trajectory Prediction Guided by Textual Descriptions", \textbf{ECCV}, 2024.}
    \item {Chi et al, ``Multi-Modal Representation Learning with Tactile Modality", \textbf{IROS}, 2024.}
    \item {Kim et al, ``Higher-order Relation Reasoning for Trajectory Prediction", \textbf{CVPR}, 2024.}
    \item {Chi et al, ``AdamsFormer for Spatial Action Localization in the Future", \textbf{CVPR}, 2023.}
    \item {Xu et al, ``Uncovering the Missing Pattern: Unified Framework Towards Trajectory Imputation and Prediction", \textbf{CVPR}, 2023.}
    \item {Chi et al, ``Pose Relation Transformer: Refine Occlusions for Human Pose Estimation", \textbf{ICRA}, 2023.}
    \item {Chi et al, ``InfoGCN: Representation Learning for Human Skeleton-based Action Recognition", \textbf{CVPR}, 2022.}
    \item {Chi et al, ``A Large-scale Annotated Mechanical Components Benchmark for Classification and Retrieval Tasks with Deep Neural Networks", \textbf{ECCV}, 2020.}
\end{cvitems}
}


\end{cventries}
