%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
\cventry
{AI/ML Resident} % Job title
{Apple Inc.} % Organization
{Cupertino, CA, USA} % Location
{Jul 2024 - } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item Conducted multi-modal perception research as part of the Siri perception team.
    % \item Integrated AI models into commercial products, leading to a 21\% action recognition performance improvement in surveillance system.
\end{cvitems}
}
% \vspace{-.5em}


\cventry
{AI Researcher} % Job title
{Hanwha Vision America} % Organization
{Santa Clara, CA, USA} % Location
{Jan - June 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item Conducted research in advanced human pose estimation and activity recognition, enhancing surveillance camera capabilities.
    \item Developed machine learning models to accurately predict human activities, significantly improving detection accuracy and reducing false positives.
    % \item Integrated AI models into commercial products, leading to a 20\% action recognition performance improvement in surveillance system.
\end{cvitems}
}
% \vspace{-.5em}


\cventry
{ML Research Intern} % Job title
{Toyota Research Institute} % Organization
{Los Altos, CA, USA} % Location
{May - Aug 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item Led a project on multi-modal representation learning for robotics, achieving advancements
        in aligning language, vision, and tactile sensor.
    \item Published a comprehensive dataset comprising language descriptions, tactile images, and visual captures of robotic interactions, facilitating enhanced robot sensory perception and interaction studies.
\end{cvitems}
}
% \vspace{-.5em}

\cventry
{CV Research Intern} % Job title
{Honda Research Institute} % Organization
{San Jose, CA, USA} % Location
{Jan - May 2023 \& May - Aug 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item Led a research project that transformed language descriptions into human motion using LLMs, establishing a new benchmark in the field.
    \item Developed a specialized VQ-diffusion model for text-to-human motion generation, focusing on accurately predicting long-term movements.
    \item Conducted pioneering research in future action forecasting and trajectory prediction for autonomous vehicles, resulting in two patents and significant advancements in vehicle safety and navigation systems.
    \item Introduced an algorithm capable of predicting future action locations by integrating NeuralODE with the Transformer for enhanced accuracy.
\end{cvitems}
}
% \vspace{-.5em}

\cventry
{Graduate Research Assistant} % Job title
{Convergence Design Lab, Purdue University} % Organization
{West Lafayette, IN, USA} % Location
{Aug 2018 - Dec 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item Advanced research in human action perception, pose estimation, and 3D computer vision, yielding numerous peer-reviewed publications and patents.
    \item Directed a team to innovate a 3D pose estimation algorithm from video, drastically enhancing both accuracy and processing speed.
    \item Developed a 3D object generation model utilizing GAN, focusing on the precise definition of geometrical features.
    \item Proposed an algorithm for skeleton-based action recognition that integrates self-attention mechanisms with graph-convolutional networks to capture human topology effectively.
\end{cvitems}
}
% \vspace{-.5em}

\cventry
{Software Engineer \& CEO} % Job title
{HeumLabs Corporation} % Organization
{Seoul, South Korea} % Location
{Sep 2016 - Dec 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item Founded and led a startup developing an office automation system, securing initial
        funding and overseeing the product development lifecycle.
    \item Achieved a successful market entry, with the system adopted by over 150 businesses within the first year.
%\item {Designed a back-end system and database for customer web-service which automatically collects and integrate financial and personal data. (\textit{Relevant patent: [\textbf{P1}]})}
\end{cvitems}
}

\cventry
{Undergraduate Research Assistant} % Job title
{Knowledge-based Design Lab, Yonsie University} % Organization
{Seoul, South Korea} % Location
{Jan. - Aug. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Advanced research in explainable AI within 3D computer vision by analyzing the role of individual parts in classification, utilizing prediction difference analysis for deeper insights.
\end{cvitems}
}

% \vspace{-.5em}
%\cventry
%{Republic of Korea Army} % Organization
%{Mechanic and Squad leader} % Job title
%{Inje, South Korea} % Location
%{Apr. 2011 – Jan. 2013} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Conducted maintanance of military weapons and equipment including firearms and vehicles.}
%\item {Led a squad as a squad leader; honored as a distinguished soldier.}
%\end{cvitems}
%}

%------------------------------------------------

\end{cventries}
